Untitled

### 2018-08-20 PaperCode.Rmd
Remove Bootstrap
The bootstrap process does not create better models. As a result I am going to remove it from the final predictive model and just use the mean models method.

---
title: "Untitled"
author: "Jonathan Bourne"
date: "9 August 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---
Mang en natt har jeg sittet opp og skrevet dype romaner paa dette skrivebordet. Det er pent brukt, men har gitt meg graa haar. Det er som min Moby Dick, jeg har aldri helt klart aa temme det, boken er halvskrevet, hodet fult, hjertet tomt. Derfor maa det bort, kona orker ikke at jeg sitter oppe og stirrer paa uskrevne linjer i min moleskinen mer.

@@

This chunk processes all the areas and combines into a single dataframe
It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
```{r}
#creates a data frame called DATAdf
suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))
rm(OAandPstCd)
```

@@

sum(LostLowUse$Lost)

ONSPD <- read_csv(file.path("/home/jonno/Dropbox/SSE/Empty Homes/ONSPD",
                            "ONS_Postcode_Directory_Latest_Centroids.csv"))

LADconv <- read_csv(file.path(AddGeog, 
                              "Local_Authority_Districts_December_2016_Names_and_Codes_in_the_United_Kingdom.csv")) %>%
  select(LAD11CD=LAD16CD, LAD11NM = LAD16NM)

test <- ONSPD %>%
  select(Postcode = pcd, LSOA11CD = lsoa11, MSOA11CD = msoa11, LAD11CD = oslaua, OA11CD = oa11,Country_code = ctry, Region =  rgn) %>%
  filter(grepl("(E92000001)|(W92000004)", Country_code)) %>%
  left_join(LADconv) %>%
  filter(!is.na(LSOA11CD))

test2 <- test  %>%
  filter(is.na(LSOA11CD))

map_dbl(.x = 1:ncol(test), ~{

  test %>% pull(.x) %>% is.na %>% sum

@@

#Create a data frame of LSO
PriceCounts <-prices %>%
  filter(X5 %in% c("D", "S", "T", "F")) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n()) %>%
  arrange(counts)
##The subsampling is 1/10 of the number of homes in each LSOA, this stops crashes
PriceCounts<- EW2 %>%
  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
  left_join(.,PriceCounts, by = "LSOA11CD") %>%
  mutate(counts = ifelse(is.na(counts), 0, counts),
         Homes2 = Homes/10) %>%
  filter(counts!=0)

#Create a list of price vectors by LSOA
#This process can take a while
setwd(basewd)
if(file.exists("LSOAPriceList2.rds")){

@@

if(file.exists("AllDataQuartiles.rds")){

@@

  AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, 
                                     PriceCounts2$LSOA11CD, 
                                     PriceCounts2$Homes2, 
                                     samples = 501) #change to 1 for a quicker solution has no effect on outcome

@@

rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary);rm(LSOAPriceList)

@@

@@

##Non-Dataset LADs
This bootstrapping is done to get the data needed to predict across the whole of Wngland and Wales
```{r}
#Filter out all the LADs for the data we have, ake dataframe that can be sampled
AllOtherLADsdf <- EW2 %>% rename(LSOA11CD = ECODE) %>%
  filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
  select(LSOA11CD:Pop, MSOA11CD, LAD11CD, LAD11NM)%>%
  mutate(LowUse = 0) 
#Bootstrap
setwd(file.path(basewd, "BootstrapAllLADs"))
BootstrapAllData(AllOtherLADsdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")

@@

@@

```{r}
#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(Class = CountryClass)

@@

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio2") +
    facet_wrap(.~Area) +
  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
SaveFig("ClassdiffAllData.pdf")

@@

setwd(file.path(basewd, "VOA data"))

#Creates Tourism dataframe at LSOA level
Tourism <- read_delim("uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv", 
                          delim = "*", col_names = F) %>%
  mutate(X15 = gsub(" ", "", X15)) %>%
  left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
  #filter(!is.na(LAD11CD)) %>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
         Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
   group_by(MSOA11CD) %>% #Have X6 as a grouping variable to 
  summarise(Tourism = n(),
            Guest = sum(Guest),
            Hotel = sum(Hotel))  %>%
  left_join(., MSOAtoLAD, by="MSOA11CD")

 MSOAAdjacency <- readShapeSpatial(file.path(basewd,"/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
                                             "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))

 test <- poly2nb(MSOAAdjacency)

 MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)

#Add MSOA codes so that they are added as the vertex names
colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd

MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")

MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
names(MSOAEgoList1) <- get.vertex.attribute(MSOAgraph, "name")

MSOAEgoList2 <- ego(MSOAgraph, 2) %>%map(~names(.x))
names(MSOAEgoList2) <- get.vertex.attribute(MSOAgraph, "name")

 TourismMSOAEgo2 <- MSOAEgoList2 %>% map_df(~{
    Tourism %>%
      filter(MSOA11CD %in% .x) %>%
      summarise(Ego2Tourism = sum(Tourism),
                Ego2Guest = sum(Guest),
                Ego2Hotel = sum(Hotel),
                Ego2Homes = sum(Homes))
 }) %>% mutate(Ego2TourismDens = Ego2Tourism/Ego2Homes,
               Ego2GuestDens = Ego2Guest/Ego2Homes,
               Ego2HotelDens = Ego2Hotel/Ego2Homes,
               MSOA11CD = names(MSOAEgoList1))

 TourismMSOAEgo1 <- MSOAEgoList1 %>% map_df(~{
    Tourism %>%
      filter(MSOA11CD %in% .x) %>%
      summarise(Ego1Tourism = sum(Tourism),
                Ego1Guest = sum(Guest),
                Ego1Hotel = sum(Hotel),
                Ego1Homes = sum(Homes))
 }) %>% mutate(Ego1TourismDens = Ego1Tourism/Ego1Homes,
               Ego1GuestDens = Ego1Guest/Ego1Homes,
               Ego1HotelDens = Ego1Hotel/Ego1Homes,
               MSOA11CD = names(MSOAEgoList1))

Tourism <- Tourism %>%
  left_join(TourismMSOAEgo1, ., by = "MSOA11CD") %>%
  left_join(., TourismMSOAEgo2, by = "MSOA11CD") %>%
  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
         Hotel = ifelse(is.na(Hotel), 0, Hotel),
         Guest = ifelse(is.na(Guest), 0, Guest))

rm(MSOAAdjacency);rm(test);rm(MSOAAdjMat); rm(MSOAgraph); rm(MSOAEgoList1);rm(MSOAEgoList2); rm(TourismMSOAEgo1);rm(TourismMSOAEgo2)

@@

```{r}
LADModelData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapMSOA"))
LADMean <- MeanModelData(LADModelData, "LAD") %>%
  mutate(TourismDensityRank = rank(TourismDensity, ties.method = "max"),
         LowUseType =case_when(
    "TRUE"==HighLUP & "TRUE" ==HighVal ~ 1, # All high
    "TRUE" == HighLUP & "FALSE" ==HighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==HighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==HighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  LowUseAfford =case_when(
    "TRUE"==HighLUP & AffordRank>=0.5 ~ 1, # All high
    "TRUE" == HighLUP & AffordRank<0.5 ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & AffordRank>=0.5 ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor)  %>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")

#Amount of variance in the bootstrap samples 
#HighVal varies whilst HighLUP is fixed. However, in both of them the variables change as the affordability ratio varies. Not sure if it varies enough to change much though!
LADRefAverages <- LADModelData %>%
  group_by(LAD11CD) %>%
  summarise(HighVal = mean(ifelse(HighVal==TRUE,1,0)),
            HighLUP = mean(ifelse(HighLUP==TRUE,1,0)),
            Afford = mean(AffordRatio),
            Affordsd = sd(AffordRatio)) %>%
  left_join(., MSOAtoLAD %>% select(LAD11CD, LAD11NM)%>% distinct)

@@

@@

```{r}
MSOAModelData <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapMSOA")) 
MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max")) %>%
  left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatioScale2,
                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff, LADMeanMedianRatio = MeanMedianRatio,
                   LowUseType), by = "LAD11CD") %>%
  mutate(BothHighLUP =case_when(
    "TRUE"==HighLUP & "TRUE" ==LADHighLUP ~ 1, # all high
    "TRUE" == HighLUP & "FALSE" ==LADHighLUP ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighLUP ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighLUP ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  BothHighVal =case_when(
    "TRUE" ==HighVal & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighVal & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighVal & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighVal & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  MSOALUPLADVal =case_when(
    "TRUE" ==HighLUP & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighLUP & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor
           )

@@

Plots that help explain the data seperation
```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD"))  %>%group_by(type)%>% mutate(Eg2 = percent_rank(Ego2TourismDens)) %>% ungroup %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Rank") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighLUP.pdf")

bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Is the median LUP price higher than the Median price of all properties", x = "Affordability Rank", y = "Tourism Density") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighVal.pdf")

@@

```{r}
#Create sample
set.seed(1235)
LADHighValResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")
set.seed(1235)
LADHighLUPResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighLUP")

#Create a load of classifiers
LADModels <- bind_rows(LinearClassifierCombiner(LADMean,  "HighVal", Formulas, LADHighValResample),
                       LinearClassifierCombiner(LADMean,  "HighLUP", Formulas, LADHighLUPResample)) %>%
MarkModels

@@

LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,2))

@@

LADMODOut %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))
LADMODOut2 %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))

@@

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", HighValResample, Formulas[[4]])  %>% filter(term !="(Intercept)")
MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
MSOAMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", MSOAHighLUPResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
MSOAMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

MSOAMODOut %>%
  select(-statistic, -std.error) %>%
  group_by(term) %>%
  summarise_all(funs(mean, median))

@@

using the most sucessful model formula I then use the Bootstrap data to create 501 models then majority vote the response variable.
This creates a model with an overall lower accuracy but also a smaller standard deviation

set.seed(1235)
LADHighValResample200 <- vfold_cv(LADMean, v = 5, repeats = 200, strata = "HighVal")
test <- LADMean %>% mutate(Reference = HighVal) %>%
  ResampledModelPerf(., LADHighValResample200, Formulas[[2]])

set.seed(1235)

TestResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")

TestResample <- vfold_cv(LADMean, v = 5, repeats = 100, strata = "HighVal")
LADModelData2 <- LADModelData %>%
  filter(ID<102)

setwd(basewd)
if(file.exists("LADBootVoteModel.rds")){

  LADBootVoteModel <- readRDS("LADBootVoteModel.rds")

  }else{
    LADBootVoteModel <- 1:100 %>% map_df(~{ 
       print(.x)
        trainrows <- rsample2caret(TestResample)$index[[.x]]
        testrows <-  rsample2caret(TestResample)$indexOut[[.x]]

>>>>

---
title: "Untitled"
author: "Jonathan Bourne"
date: "9 August 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

schedule 2 part 5 section

@@

This chunk processes all the areas and combines into a single dataframe
It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
```{r}
#creates a data frame called DATAdf
suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))

@@

sum(LostLowUse$Lost)
```

@@

#Create a data frame of LSO
PriceCounts <-prices %>%
  filter(X5 %in% c("D", "S", "T", "F")) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n()) %>%
  arrange(counts)
##The subsampling is 1/10 of the number of homes in each LSOA, this stops crashes
PriceCounts<- EW2 %>%
  select(LSOA11CD, Homes, Pop, LAD11CD, MSOA11CD) %>%
  left_join(.,PriceCounts, by = "LSOA11CD") %>%
  mutate(counts = ifelse(is.na(counts), 0, counts),
         Homes2 = Homes/10) %>%
  filter(counts!=0) %>%
  left_join(IncomeEst %>% select(MSOA11CD, Yearly.income))

#Create a list of price vectors by LSOA
#This process can take a while
setwd(DataFolder)
if(file.exists("LSOAPriceList2.rds")){

@@

 #Price Quartiles
 if(file.exists("AllDataQuartiles.rds")){

@@

  AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, 
                                     PriceCounts2$LSOA11CD, 
                                     PriceCounts2$Homes2, 
                                     samples = 100) #change to 1 for a quicker solution has no effect on outcome

@@

#Affordability Quartiles

if(file.exists("LSOAAffordList.rds")){

  LSOAAffordList <- readRDS("LSOAAffordList.rds")

  LSOAAffordList<- 1:nrow(PriceCounts) %>%
  map(~{
    print(.x)
    LSOAPriceList[[.x]]/PriceCounts$Yearly.income[.x]

  })
 names(LSOAAffordList) <- PriceCounts$LSOA11CD
  saveRDS(LSOAAffordList, "LSOAAffordList.rds")

 #Price Quartiles
 if(file.exists("AllDataAffordQuartiles.rds")){

  AllDataAffordQuartiles <- readRDS("AllDataAffordQuartiles.rds")

}else{
  #Subset list to only the LADs used in analyis
  LSOAAffordList2 <- LSOAAffordList[names(LSOAAffordList) %in% unique(DATAdf$LSOA11CD)]
  PriceCounts2 <- PriceCounts %>%
    filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))

   AllDataAffordQuartiles <- StratifiedBoot(LSOAAffordList2, 
                                     PriceCounts2$LSOA11CD, 
                                     PriceCounts2$Homes2, 
                                     samples = 100) #change to 1 for a quicker solution has no effect on outcome

  saveRDS(AllDataAffordQuartiles, "AllDataAffordQuartiles.rds")

  rm(list = c("LSOAAffordList2", "PriceCounts2"))

AllDataAffordQuartilesSummary <-  AllDataAffordQuartiles %>%
  summarise_all(funs(mean, sd))

#Add the balanced quartiles on to the prices.
prices <- prices %>%
  left_join(select(PriceCounts, LSOA11CD, Yearly.income)) %>%
  mutate(Affordability = X2/Yearly.income) %>%
  select(-Yearly.income ) %>%
  mutate(CountryAffordClass = cut(Affordability, AllDataAffordQuartilesSummary[2:4] %>% c(0,., Inf), 
                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
                              right = F) %>% fct_relevel(., "Upper", after = 3))

rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary);rm(LSOAPriceList);rm(AllDataAffordQuartiles);rm(AllDataAffordQuartilesSummary);rm(LSOAAffordList)

@@

Affordability Bootstrap
```{r}
setwd(file.path(basewd, "BootstrapAffordQuartiles"))
BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = c("AffordClass", "CountryAffordClass"))
#BootStrapAffordQuartiles <- LoadBootstrapData()
#BootStrapQuartiles2 <- BootStrapQuartiles

BootStrapQuartiles<- BootStrapAffordQuartiles
```

@@

##Non-Dataset LADs
This bootstrapping is done to get the data needed to predict across the whole of Wngland and Wales
```{r}
#Filter out all the LADs for the data we have, ake dataframe that can be sampled
AllOtherLADsdf <- EW2 %>%
  filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
  select(LSOA11CD:Pop, MSOA11CD, LAD11CD, LAD11NM)%>%
  mutate(LowUse = 0) 
#Bootstrap
setwd(file.path(basewd, "BootstrapAllLADs"))
BootstrapAllData(AllOtherLADsdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")

@@

##Old prices Bootstrap

This is to calculate % change
```{r}

if(length(list.files(file.path(basewd, "BootstrapMSOAOldPrices")))==0){
prices <- prices2
DATAdf2 <- DATAdf %>% mutate(LowUse = 0)
prices <- readRDS(file.path(DataFolder,"pricesOld.rds")) %>% mutate(CountryClass = 1, Affordability = 1, CountryAffordClass = 1)
setwd(file.path(basewd, "BootstrapMSOAOldPrices"))
BootstrapAllData(DATAdf2, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
rm(DATAdf2)
prices<- prices2
rm(prices2)
}

@@

```{r}
#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass = CountryAffordClass, ID, LowUse, Homes)

@@

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020, AffordClass) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032, AffordClass) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class, CountryClass) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio1") +
    facet_wrap(.~Area) +
  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
SaveFig("ClassdiffAllData.pdf")

@@

```{r}
if(file.exists(file.path(DataFolder, "Tourism.rds"))){

  Tourism <- readRDS(file.path(DataFolder, "Tourism.rds"))
}else{

  suppressMessages(source(file.path(SubCode, "LoadProcessTourism.R")))

}
```

```{r}
test <- list.files(file.path(basewd, "BootstrapMSOAOldPrices"), full.names = TRUE) %>%
    map_df(~readRDS(.x)) %>% select(MSOA11CD,LAD11CD, ID, MSOAHomesMedian:LADHomesMean) %>% 
  set_names(c(names(.)[1:3], paste0(names(.)[-c(1:3)], "Old")))

  group_by(LAD11CD) %>%
      summarise(HomesMedian = first(LADHomesMedian),
                HomesMean = first(LADHomesMean)) %>% 
  rename(LADHomesMedianOld = HomesMedian,
         LADHomesMeanOld = HomesMean)

test2 <- left_join(LADMean, test) %>%
  mutate(PercChange = (HomesMedian-LADHomesMedianOld)/LADHomesMedianOld,
         PercChange = (HomesMean-HomesMeanOld)/HomesMeanOld)

t.test(test2$LADHomesMedianOld, test2$HomesMedian, alternative = "less")

test2 %>%
  ggplot(aes(x = HomesMedian, y = LADHomesMedianOld))

test2 %>%
  ggplot(aes(x = PercChange)) + geom_density()

test2%>%
  ggplot(aes(x = PercChange, y = AffordRatio)) + geom_point()

cor(test2$AffordRatio, test2$PercChangeMean)

MSOAtest <- list.files(file.path(basewd, "BootstrapMSOAOldPrices"), full.names = TRUE) %>%
    map_df(~readRDS(.x)) %>% select(MSOA11CD,LAD11CD, ID, MSOAHomesMedian:LADHomesMean) %>% 
   group_by(MSOA11CD) %>%
      summarise(HomesMedianOld = first(MSOAHomesMedian),
                HomesMeanOld = first(MSOAHomesMean)) %>% 
  left_join(MSOAMean, .) %>%
  mutate(PercChange = (HomesMedian-HomesMedianOld)/HomesMedianOld,
         PercChangeMean = (HomesMean-HomesMeanOld)/HomesMeanOld)

cor(MSOAtest$AffordRatio, MSOAtest$PercChangeMean)

MSOAtest %>%
  ggplot(aes(x = PercChange)) + geom_density()

MSOAtest%>%
  ggplot(aes(x = log(TourismDensity+1), y = percent_rank(PercChange), colour = HighLUP)) + geom_point()

@@

```{r}
LADModelData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapMSOA"))
LADMean <- MeanModelData(LADModelData, "LAD") %>%
  mutate(TourismDensityRank = rank(TourismDensity, ties.method = "max"),
         TourismDensity = TourismDensity*1000, #Makes the coefficients easier
         LowUseType =case_when(
    "TRUE"==HighLUP & "TRUE" ==HighVal ~ 1, # All high
    "TRUE" == HighLUP & "FALSE" ==HighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==HighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==HighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  LowUseAfford =case_when(
    "TRUE"==HighLUP & AffordRank>=0.5 ~ 1, # All high
    "TRUE" == HighLUP & AffordRank<0.5 ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & AffordRank>=0.5 ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
    HighFinance = factor("TRUE"==HighVal & "TRUE"==HighLUP, levels = c("FALSE", "TRUE"))   )  %>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")

@@

  #Relationship between Price change and affordability
#From this we can see that areas with the most growth are the most unaffordable
      cor(LADMean$PercChange, LADMean$AffordRatio)
#However this only really tells us that the most expensive areas previously continue to be the most expensive  
      cor(LADMean$HomesMeanOld, LADMean$HomesMean)

@@

```{r}
MSOAModelData <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapMSOA")) 
MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max"),
         TourismDensity = TourismDensity*1000) %>% #Makes the coefficients easier
  left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatioScale2,
                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff, LADMeanMedianRatio = MeanMedianRatio,
                   LowUseType), by = "LAD11CD") %>%
  mutate(BothHighLUP =case_when(
    "TRUE"==HighLUP & "TRUE" ==LADHighLUP ~ 1, # all high
    "TRUE" == HighLUP & "FALSE" ==LADHighLUP ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighLUP ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighLUP ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  BothHighVal =case_when(
    "TRUE" ==HighVal & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighVal & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighVal & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighVal & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  MSOALUPLADVal =case_when(
    "TRUE" ==HighLUP & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighLUP & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
       HighFinance = factor("TRUE"==LADHighVal & "TRUE"==HighLUP, levels = c("FALSE", "TRUE"))     )

  #Relationship between Price change and affordability
#From this we can see that areas with the most growth are the most unaffordable
      cor(MSOAMean$PercChange, MSOAMean$AffordRatio)
#However this only really tells us that the most expensive areas previously continue to be the most expensive  
      cor(MSOAMean$HomesMeanOld, MSOAMean$HomesMean)

@@

Plots that help explain the data seperation

```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD"))  %>%group_by(type)%>% mutate(Eg2 = percent_rank(Ego2TourismDens)) %>% ungroup %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Rank") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighLUP.pdf")

bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighVal)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Is the median LUP price higher than the Median price of all properties", x = "Affordability Rank", y = "Tourism Density") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighVal.pdf")

@@

```{r}
#Create sample
set.seed(1235)
LADHighValResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")
set.seed(1235)
LADHighLUPResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighLUP")
set.seed(1235)
LADHighFinanceResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighFinance")

#Create a load of classifiers
LADModels <- bind_rows(LinearClassifierCombiner(LADMean,  "HighVal", Formulas, LADHighValResample),
                       LinearClassifierCombiner(LADMean,  "HighLUP", Formulas, LADHighLUPResample),
                       LinearClassifierCombiner(LADMean,  "HighFinance", Formulas, LADHighFinanceResample)) %>%
MarkModels

@@

LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
 # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,3))

@@

LADMODOut %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median, sd))
LADMODOut2 %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median, sd))

@@

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", MSOAHighValResample, Formulas[[2]])  %>% filter(term !="(Intercept)")
MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
MSOAMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", MSOAHighLUPResample, Formulas[[4]]) %>% filter(term !="(Intercept)")
MSOAMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

MSOAMODOut %>%
  select(-statistic, -std.error) %>%
  group_by(term) %>%
  summarise_all(funs(mean, median)) %>%
  mutate(estimate = exp(estimate_mean))

@@

using the most sucessful model formula I then use the Bootstrap data to create 501 models then majority vote the response variable.

The Bootstrap model doesn't provide any more information. despite the pertubations it tends to always predict certain LADs incorrectly and others correctly. This means that the bootstrap predictions are not sufficiently independent to make the proocess worthwhile.

```{r}
#Creates a boots model which can be analysed
